Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2022-03-04 results.tex
Numerical methods - Update
I filled the gaps and put the plots in one as requested.

The Kirkwood sphere [Kirkwood1934] is a standard benchmarck for the Poisson-Boltzmann equation in molecular electrostatics. 
Here, we considered a spherical cavity with radius $R=X$ \AA, with three charges ($q_1$=a, $q_2$=b, and $q_3$=c) placed at $\mathbf{x}_1=(x_1,y_1,z_1)$, $\mathbf{x}_2=(x_2,y_2,z_2)$, and $\mathbf{x}_3=(x_3,y_3,z_3)$.
Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}=XX$ kcal/mol). 
In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\linewidth]{BEM_BEM_Sphere_const_coeff_error.png}
  \includegraphics[width=0.45\linewidth]{FEM_BEM_Sphere_const_coeff_error.png}
  \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_error.png}
  \caption{Error for the Kirkwood sphere. Can we put all these in a single plot and in log-log? No need for percentage, I think.}
  \label{fig:error_sphere}
\end{figure}

@@

As a more realistic test, we assessed the performance of the standard and hybrid FEM-BEM coupling techniques against a purely BEM implementation for arginine [cite arg]. 
We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper [Rocchia].
These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.

@@

\begin{figure}
\centering
\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_time.png}
\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_time.png}
\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity. (1) fix title, (2) can we put them in a single plot, (3) maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
\label{fig:arg_contant_time}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_iter.png}
\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_iter.png}
\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_iter.png}
\caption{Iteration count for arginine with a constant permittivity. (1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations? maybe we should present the total count?}
\label{fig:arg_contant_iter}
\end{figure}

@@

In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom [earlier papers], which has shown enhanced accuracy in some applications, like binding energy calculations (check) [Alexov].
In this setting, we define a density function $\rho$ as
%
\begin{equation}
\rho
\end{equation}
%
where the sum is over the atoms of the solute, and we used $\sigma$=1. Then, we can compute the permittivity as
%
\begin{equation}
\epsilon
\end{equation}
%

>>>>

The Kirkwood sphere [Kirkwood1934] is a standard benchmarck for the Poisson-Boltzmann equation in molecular electrostatics. 
Here, we considered a spherical cavity with radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.33752347454015$ kcal/mol). 
In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
For the hybrid FEM-BEM coupling approach, we used $\tau$=10.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{Sphere_const_coeff_error.png}
%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_iter.png}
%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_time.png}
  \caption{Error for the Kirkwood sphere.}
  \label{fig:error_sphere}
\end{figure}

@@

As a more realistic test, we assessed the performance of the standard and hybrid FEM-BEM coupling techniques against a purely BEM implementation for arginine [cite arg]. 
We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper [Rocchia].
These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
For the hybrid FEM-BEM coupling approach, we used $\tau$=10.

@@

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) 
maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
\label{fig:arg_contant_time}
\end{figure}

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_iter.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
\caption{Iteration count for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations? maybe we should present the total count?
}
\label{fig:arg_contant_iter}
\end{figure}

@@

In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom [earlier papers], which has shown enhanced accuracy in some applications, like binding energy calculations (check) [Alexov].
In this setting, we define a density function $\rho$ depending on position $r$ as
%
\begin{equation}
\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
\end{equation}
%
where the product is over the atoms of the solute, $R_i$ is the vdW
radius of atom i and we used $\sigma$=1. Then, we can compute the permittivity as
%
\begin{equation}
\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
\end{equation}
%
